\section{Meeting with supervisor - May 8th}
\begin{tabular}{ll}
    \textbf{Date:} & Thursday, May 8th 2025 \\
    \textbf{Time:} & 12.00 - 13.00\\
    \textbf{Location:} & F424 Ankeret, NTNU Ålesund \\
    \textbf{Participants:} & Birgitte Thoresen, Chris Sivert Sylte, Vegard Mytting and Saleh Abdel-Afou Alaliyat\\
\end{tabular}

\vspace{0.5cm}

\subsection{Agenda}

\begin{itemize} 
    \item Review of work completed since the last meeting
    \item Review of the second version of the report
    \item Technical questions regarding submission
\end{itemize}

The meeting began with a demonstration of the nearly completed application. The demo showcased functionality with two chessboards and two cameras. The application operated as expected, and both boards were displayed correctly on the front-end interface.

However, there was a noticeable delay in registering moves. Typically, a pawn move should be detected within five seconds, but it currently takes around ten. This delay may be due to several factors, with the supervisor suggesting that the limited capacity of the test computer could be a contributing cause. Improved performance is expected on a more powerful machine.

A known issue is that the application crashes when a player performs the special move en passant. When this occurs, the machine learning model shuts down. Despite this, the second board continues to function correctly and is still recorded.

Testing of the machine learning model revealed a performance accuracy of 90.6\%, while the model itself has a theoretical accuracy of 96\%. This discrepancy will be discussed in the report’s discussion section. 

As the application is now functioning as intended, the supervisor recommended presenting it to the product owner for feedback. This could be arranged through a meeting or by sending a recorded demonstration via email for review.

The supervisor emphasized focusing on the report moving forward. The last reviewed version had a solid structure but lacked updated sections on results and discussion. The team should now prioritize completing these sections, as well as the conclusion. The discussion should also reflect on the development process and the final product.

An additional chapter on Societal Impact should be included after the conclusion. This should cover potential climate, health, social, and economic implications. The machine learning test data can either be added as an appendix or submitted as a separate file. If included in the appendix, the results need to be well-formatted. The team should consider how much detail is necessary for the reader to understand the results.

The supervisor advised using the guidelines available on Blackboard and referring to previous bachelor submissions for support with the writing process.

For multiple reasons, the final presentation should feature a pre-recorded demonstration instead of a live one. This will ensure a smoother and more reliable presentation. The video should clearly show how the application works and allow for voice-over narration during the presentation.

\subsection{Other}
The next meeting is scheduled for Tuesday, May 13th at 12:00 in room A434 (Ankeret). This meeting also marks the deadline for submitting the final version of the report to be reviewed, and it will be the last meeting with the supervisor.

The final version of the report must be submitted in Inspera by Tuesday, May 20th at 12:00. It is important that the team forms groups correctly and ensures proper submission in accordance with the official guidelines.