\section{Meeting with supervisor - April 4th}
\begin{tabular}{ll}
    \textbf{Date:} & Friday, April 4th 2025 \\
    \textbf{Time:} & 12.00 - 12.30\\
    \textbf{Location:} & A433 Ankeret, NTNU Ålesund \\
    \textbf{Participants:} & Birgitte Thoresen, Chris Sivert Sylte, Vegard Mytting and Saleh Abdel-Afou Alaliyat\\
\end{tabular}

\vspace{0.5cm}

\subsection{Agenda}

\begin{itemize} 
    \item Review of work completed since the last meeting
    \item Focus areas for the upcoming weeks
    \item Other items
\end{itemize}

The meeting began with a demonstration of the frontend application. The frontend is now successfully connected to the WebSocket and is capable of replicating chess moves. The WebSocket streams a sequence of moves to the frontend, which then visualizes them on a digital chessboard. Additional features demonstrated included a PGN (Portable Game Notation) display and integrated video footage from a connected camera. The supervisor reviewed the progress and describing it as great work.

Since the previous meeting, the group has also conducted initial user testing on the wireframe design. In order to obtain diverse and relevant feedback, the group involved both computer engineering students and chess players. Users were asked to evaluate aspects such as functionality and design. So far, the feedback has been largely positive, with the primary suggestion being improvements to the application's user experience (UX). These findings were presented to the supervisor, who emphasized the importance of user testing in achieving a high-quality outcome.

The supervisor advised the team to begin focusing more heavily on the written project report. The group has already started drafting the report, with initial sections for the introduction and theoretical background completed. The next priority is the methodology section. Given that the Easter break is approaching, the supervisor recommended using the time after the holiday to make substantial progress on the report.

\subsection{Other}
The next meeting, originally scheduled during the Easter break, has been rescheduled to April 24 at 10:00 (in three weeks).
