\section{Meeting with supervisor - March 21th}
\begin{tabular}{ll}
    \textbf{Date:} & Friday, March 21th 2025 \\
    \textbf{Time:} & 12.00 - 12.30\\
    \textbf{Location:} & A433 Ankeret, NTNU Ålesund \\
    \textbf{Participants:} & Birgitte Thoresen, Chris Sivert Sylte, Vegard Mytting and Saleh Abdel-Afou Alaliyat\\
\end{tabular}

\vspace{0.5cm}

\subsection{Agenda}

\begin{itemize} 
    \item Review of work since last meeting 
    \item Review of meeting with product owner 
    \item Present wireframes 
    \item Plan forward 
    \item Documentation of used libraries 
\end{itemize}

Since the last meeting with the supervisor, the group successfully implemented functionality to find the center of each tile on the chessboard. The model correctly identifies the center, although the x-corners are slightly inaccurate. Currently, the model reloads the centers every frame — this is primarily for testing purposes, as reloading each frame is computationally expensive. The supervisor suggested calculating the outer corners first and then determining the rest based on these.

Progress was also made on a functional display of a chess game. The display receives input via the console using commands such as \textit{makeMove("e4")}, which corresponds to the move "e4". This functionality relies on the Chess.js library, which handles chess rules and game logic.

The wireframes and UML diagrams were presented to the supervisor. The wireframes illustrate the application's design and key interactions. The group has planned to test the wireframes with the university's chess team, "NTNUI Sjakk," next Monday. The supervisor responded positively to both the wireframes and the overall concept.

Some other bachelor groups were required to document the libraries used in their projects by their supervisor. For this report, the libraries should also be documented — briefly and at a higher level. Instead of detailing the internal workings of each library, the focus should be on how and where they have been used in the project.

All sources referenced in the report must be cited properly. This includes articles, reports, images, and figures. Images can be cited either through captions that include URLs or as general website references. The key is to maintain consistency throughout the report.

The final report is due on May 20th. The supervisor will review the report one week in advance but is also available to provide feedback at earlier stages. The main deliverable is the report itself, which should include project results, illustrative images, and a “how to use” manual. Creating a demo video could also be beneficial for the final bachelor thesis presentation.

