\section{Meeting with supervisor - May 13th}
\begin{tabular}{ll}
    \textbf{Date:} & Tuesday, May 13th 2025 \\
    \textbf{Time:} & 12.00 - 13.00\\
    \textbf{Location:} & A433 Ankeret, NTNU Ålesund \\
    \textbf{Participants:} & Birgitte Thoresen, Chris Sivert Sylte, Vegard Mytting and Saleh Abdel-Afou Alaliyat\\
\end{tabular}

\vspace{0.5cm}

\subsection{Agenda}

\begin{itemize} 
    \item Review of poster
    \item Review of the third version of the report
    \item Questions about the report
    \item Focus points forward
\end{itemize}

The meeting began with a review of the poster, which is due tomorrow. Previously, the supervisor requested that the logo of our product owner, Ålesund Sjakklag, be included. In the current version, the logo is placed beside the NTNU logo in the footer. The supervisor commented that while the logo might be slightly small, the placement is acceptable. An alternative suggestion was to place the logo alongside the technologies used, but this did not fit visually. There was also uncertainty regarding whether to include the supervisor’s name on the poster. Based on examples from previous years, the supervisor is typically included.

Next, the supervisor provided feedback on the third version of the report, highlighting several areas for improvement:

\begin{itemize}
    \item The title should use the plural form: "\textit{... chess games}" instead of "\textit{... a chess game}".
    \item Remove the unused section \textit{List of code}.
    \item Terms introduced in the abstract or summary should also be defined in the main body of the report—for instance, in Section 1.1 (Background).
    \item The introduction should be expanded to include a Section 1.2 (Motivation) describing the group’s motivation for the project.
    \item Section 1.2 (Objective) should present the goals as bullet points. Start with a short introduction, then list bullet points, followed by a short concluding paragraph.
    \item In Section 2.2 (Machine Learning), the paragraph starts with "computer vision," which is not the same as machine learning—this should be corrected.
    \item Section 2.3 (Object Detection) should begin with a general explanation of object detection before introducing LeYOLO.
    \item In Section 2.3.1 (Euclidean Distance), clarify why this concept is relevant and how it is used in the project.
    \item In Section 2.5 (Project Management), explain agile methodologies before introducing Scrum. Clarify that Scrum is a framework, not a method. Including a diagram or figure would be beneficial.
    \item Section 3.2 (Project Management) should include details on documentation practices, workflow, etc. The wireframes should be moved to the Design section.
    \item Rename the subsection "Obstacles" to "Challenges." This section should cover both project-related and result-related challenges.
    \item Divide the results into separate sections for Machine Learning, API, and Frontend.
    \item The project management discussion should address deviations from the original plan and why the group chose Scrum.
    \item Testing procedures (e.g., for machine learning models, color palette, etc.) should be placed in a dedicated section titled "Testing."
    \item Include a “Feedback” section in the discussion, summarizing the product owner's review of the final product.
    \item The conclusion should extend the abstract and be approximately one page long.
\end{itemize}

The team’s focus moving forward should be on refining and finalizing the report. It's important to continuously review and improve the document during the writing process.

For the final presentation at the ceremony, the following structure was recommended:

\begin{itemize}
\item Briefly introduce the project, its problem domain, and the methods used.
\item Present the results, including a demonstration video with voiceover.
\item Reflect on the project’s outcome. Was it successful? What were the key challenges?
\item Follow a structure similar to the report: begin with the objectives and connect them to the final results.
\end{itemize}

\subsection{Other}
Any specific questions for the supervisor can be emailed to him.

Submit both the final report and the demo to the supervisor before final submission.



